Explore spatial allocation

### 2021-03-09 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
made a dataset for number of farms modeling

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

@@

# read in shp
farms_all <- ASC_bivalve %>%
  cbind(iso) %>%
  mutate(iso3c = ifelse(str_detect(comp_nm, "Jersey"), "JEY", iso3c))

@@

Now we will map the remaining countries with bivalve farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of bivalve farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
 - Lastly, if there is no evidence of marine bivalve farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia).

@@

Source: 
HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

@@

Source: 
Shellfish Hatcheries - Coastal Resource Information Management System (CRIMS) , 2019. Ministry of Forests, Lands, Natural Resource Operations and Rural Development. [Accessed November 30, 2020] https://catalogue.data.gov.bc.ca/dataset/shellfish-hatcheries-coastal-resource-information-management-system-crims

@@

```{r}
## read shapefile
ns <- st_read(file.path(path,"Canada/Nova_Scotia_Marine_Aquaculture_Sites/geo_export_fcc6f2ef-82bb-4445-98f0-a82a56cd0d00.shp"))
mapview(ns)

@@

https://servicio.pesca.mapama.es/acuivisor/
 - This is a map of all aquaculture facilities in Spain. It will not allow for download of the locations of the facilities. However, I have downloaded all of the names of each shellfish installation, with the company name, and what general location they are located in. I will filter for unique cities, and place points in each place.

@@

Source: 
Acuivisor, 2019. . Ministerio de Agricultura, Pesca Y Alimentacion, Gobierno de Espana. [Accessed December 2, 2020] https://servicio.pesca.mapama.es/acuivisor/

@@

## Jersey 
 - Government of Jersey: https://www.gov.je/SiteCollectionDocuments/Industry%20and%20finance/ID%20Mollusc%20farms%20registered%20businesses%20page%201.pdf
  - https://www.gov.je/SiteCollectionDocuments/Industry%20and%20finance/ID%20Molluscs%20farms%20registered%20businesses%20page%202%2020181030%20DM.pdf

 - 5 licensed farms (only including "mollusc farm open"): Locations estimated from maps and addresses listed 
 - Jersey Oyster Company Limited: 49.172680993306905, -2.0255193115109957
 - Seymour Oyster Company Ltd: 49.220095937386375, -2.0215887506551438
 - La Rocque Fisheries Limited: 49.169912669200976, -2.0230904378277916
 - Jersey Sea Farms: 49.242435452408536, -2.060618920921559
 - Island Dived Scallops: 49.20656011166959, -2.0158403231425996

Source: 
Fish and shellfish farming, 2020. . Government of Jersey: Information and public services for the Island of Jersey. [Accessed December 4, 2020]  https://www.gov.je/Industry/FarmingFishing/Fishing/Pages/FishFarming.aspx

 - UPDATE: This is not necessary. These companies are represented in the ASC data, but listed under the UK. I will fix this, so that we aren't double counting these farms.

```{r, evalute = F}

# farms_jey <- data.frame(lat = c(49.172680993306905, 49.220095937386375, 49.169912669200976, 49.242435452408536, 49.20656011166959),
#                         lon = c(-2.0255193115109957, -2.0215887506551438, -2.0230904378277916, -2.060618920921559, -2.0158403231425996)) %>%
#   mutate(iso3c = "JEY") %>%
#   mutate(data_quality = 4) %>%
#   mutate(action_needed = "Land mask")
# 
# write_csv(farms_jey, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_jey.csv"))
# 
# ## visualize it 
# farms_jey <-  st_as_sf(farms_jey, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_jey)

@@

Source: 
Fishing and Aquaculture, 2020. . Government of the States of Guernsey. [Accessed December 3, 2020] https://www.gov.gg/fishing#:~:text=Sea%20Fisheries%20is%20responsible%20for,one%20licensed%20site%20on%20Herm

@@

## Taiwan
- I can't find any information on the locations of shellfish farms in Taiwan, however, they have a lot of production. I will randomly place a point in the Qigu lagoon (see article). 
 - https://www.newsecuritybeat.org/2019/10/taiwan-beach-snow/

@@

Source:
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

@@

Source: 
Marine fish culture, pond fish culture and oyster culture, n.d. . Agriculture, Fisheries, and Conservation Department; The Government of the Hong Kong Special Administrative Region.  https://www.afcd.gov.hk/english/fisheries/fish_aqu/fish_aqu_mpo/fish_aqu_mpo.html

>>>>

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

@@

# read in shp
farms_all <- ASC_bivalve %>%
  cbind(iso) %>%
  mutate(iso3c = ifelse(str_detect(comp_nm, "Jersey"), "JEY", iso3c)) ## fix Jersey

@@

Now we will map the remaining countries with bivalve farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of bivalve farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - Lastly, if there is no evidence of marine bivalve farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia).

@@

Source: 
HELCOM HOLAS II Dataset: Shellfish mariculture, 2017. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

@@

Source: 
Shellfish Hatcheries - Coastal Resource Information Management System (CRIMS), 2019. Ministry of Forests, Lands, Natural Resource Operations and Rural Development. [Accessed November 30, 2020] https://catalogue.data.gov.bc.ca/dataset/shellfish-hatcheries-coastal-resource-information-management-system-crims

@@

```{r}
# library(jsonlite)
# test <- fromJSON("https://data.novascotia.ca/resource/h57h-p9mm.json")

## read shapefile
ns <- st_read(file.path(path,"Canada/Nova_Scotia_Marine_Aquaculture_Sites/geo_export_fcc6f2ef-82bb-4445-98f0-a82a56cd0d00.shp"))
mapview(ns)

@@

https://servicio.pesca.mapama.es/acuivisor/

 - This is a map of all aquaculture facilities in Spain. It will not allow for download of the locations of the facilities. However, I have downloaded all of the names of each shellfish installation, with the company name, and what general location they are located in. I will filter for unique cities, and place points in each place.

@@

Source: 
Acuivisor, 2019. Ministerio de Agricultura, Pesca Y Alimentacion, Gobierno de Espana. [Accessed December 2, 2020] https://servicio.pesca.mapama.es/acuivisor/

@@

@@

Source: 
Fishing and Aquaculture, 2020. Government of the States of Guernsey. [Accessed December 3, 2020] https://www.gov.gg/fishing#:~:text=Sea%20Fisheries%20is%20responsible%20for,one%20licensed%20site%20on%20Herm

@@

## Taiwan
- I can't find any information on the locations of shellfish farms in Taiwan. I will randomly place a point in the Qigu lagoon (see article). 
 - https://www.newsecuritybeat.org/2019/10/taiwan-beach-snow/

@@

Source:
NASO aquaculture maps collection, 2010. Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

@@

Source: 
Marine fish culture, pond fish culture and oyster culture, n.d. Agriculture, Fisheries, and Conservation Department; The Government of the Hong Kong Special Administrative Region.  https://www.afcd.gov.hk/english/fisheries/fish_aqu/fish_aqu_mpo/fish_aqu_mpo.html

### 2021-03-09 marine/explore_spatial_allocation.Rmd
made a dataset for number of farms modeling

Read in and summarise all data quality farm data 
```{r}
bivalves <- read_csv(here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "bivalve") %>%
  dplyr::select(-X1)

@@

```{r}
n_farms <- all_farms %>%
  group_by(iso3c, data_quality, group) %>%
  summarise(n_farms = n()) %>%
  ungroup() %>%
  group_by(iso3c) %>%
  mutate(avg_quality = mean(data_quality)) %>%
  ungroup()

@@

n_countries <- n_farms %>%
  group_by(data_quality, group) %>%
  summarise(n_countries = n()) %>%
  ungroup() %>%
  group_by(group) %>%
  mutate(total_countries = sum(n_countries)) %>%
  ungroup() %>%
  mutate(percent = n_countries/total_countries)

>>>>

Read in and combine all farm data 
```{r}
bivalves <- read_csv(here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "bivalve") %>%
  dplyr::select(-X1)

@@

Read in and combine all FAO tonnage data per country
```{r}
bivalves_tonnes <- read_csv(here::here("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv")) %>%
  mutate(group = "bivalve")

shrimp_tonnes <- read_csv(here::here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv")) %>%
  mutate(group = "shrimp") %>%
  filter(year == 2017)

marine_fish_tonnes <- read_csv(here::here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv")) %>%
  mutate(group = "marine_fish_general") %>%
  filter(year == 2017)

salmon_tonnes <- read_csv(here::here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv")) %>%
  mutate(group = "salmon") %>%
  filter(year == 2017)

crustaceans_tonnes <- read_csv(here::here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
  mutate(group = "crustaceans") %>%
  filter(year == 2017)

tuna_tonnes <- read_csv(here::here("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv")) %>%
  mutate(group = "tuna") %>%
  filter(year == 2017)

all_species_country_tonnes <- rbind(bivalves_tonnes, shrimp_tonnes, marine_fish_tonnes, salmon_tonnes, crustaceans_tonnes, tuna_tonnes)
```

```{r}
n_farms <- all_farms %>%
  group_by(iso3c, data_quality, group) %>%
  summarise(n_farms = n()) %>%
  ungroup()

@@

## make a dataset with the country, species type (farm type), tonnage, and # of farms, for those that score data quality %in% c(3,4,5)
sum(all_species_country_tonnes$fao_tonnes_production) # 29623515

n_farms_final <- n_farms %>%
  filter(data_quality %in% c(3,4,5)) %>%
  group_by(iso3c, group) %>%
  summarise(n_farms = sum(n_farms)) %>%
  left_join(all_species_country_tonnes, by = c("iso3c", "group")) %>%
  dplyr::select(iso3c, country, year, group, n_farms, fao_tonnes_production)
sum(n_farms_final$fao_tonnes_production) # 26812832

n_farms_tonnes_no_info <- n_farms %>%
  filter(data_quality %in% c(1, 2)) %>%
  group_by(iso3c, group) %>%
  summarise(n_farms = sum(n_farms)) %>%
  left_join(all_species_country_tonnes, by = c("iso3c", "group")) %>%
  mutate(n_farms = NA)
sum(n_farms_tonnes_no_info$fao_tonnes_production) # 2810682

26812832 + 2810682 # 29623514 # perfect

n_farms_final_final <- rbind(n_farms_final, n_farms_tonnes_no_info)
sum(n_farms_final_final$fao_tonnes_production) # 29623515

## save n_farms_final to use to make a model of farms and production
write.csv(n_farms_final_final, "data/n_farms_production_data.csv", row.names = FALSE)

Now let's do some exploration:

```{r}
n_countries <- n_farms %>%
  group_by(data_quality, group) %>%
  summarise(n_countries = n()) %>%
  ungroup() %>%
  group_by(group) %>%
  mutate(total_countries = sum(n_countries)) %>%
  ungroup() %>%
  mutate(percent = n_countries/total_countries)

test2 <- n_farms %>%
  group_by(data_quality) %>%
  summarise(n_countries = n())

countries <- data.frame(iso3c = unique(all_farms_sf$iso3c)) %>%
  mutate(country = countrycode(iso3c, origin = 'iso3c', destination = 'country.name'))
